Covid-19 Fields Survey Data Protocol

### 2023-01-15 protocol/Background_and_methods_Jan_12.qmd
need to fix labels

d<-modelplot(model1,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

e<-modelplot(model2,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

f<-modelplot(model3,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

>>>>

d<-modelplot(model1,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("1st Model")

e<-modelplot(model2,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("2nd Model")

f<-modelplot(model3,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("3rd Model")
